---
title: "Course 9 Week 4 Document"
author: "Chandramouli M"
date: "October 25, 2017"
output: ioslides_presentation
---

## Introduction to problem statement

The data set is a collection of work that is being performed on sales data for FY17 per each quarter.

- Quarter (Which quarter of FY17)
- Month (Which Month in the quarter the sale happend)
- og ( Which operating Group)
- led (Is it a GDN Led or OG led deal)
- oper (Which operating model owned or support)
- amtinm (Amount in $ Million)
- amtink (Amount in $'000)

## Data set Information

```{r salesdata, echo = TRUE, warning=FALSE, message=FALSE}
library(lattice)
indata <- read.csv("salesdata.csv", header=TRUE)
colnames(indata)[1]<- "Quarter"

names(indata)
head(indata)
```
## Functionality

This application provides information about the quarter wise and Operating group wise sales data, users has to select the Quarter and the Operating group from the provided list and submit.



```{r}
     fltr1 <- subset(indata, (indata$og == "FS" & indata$Quarter == "Q1-FY17"))
     fltr1$amtinm = as.numeric(fltr1$amtinm)
     sumval <- sum(fltr1$amtinm,indata$og == "FS" & indata$Quarter == "Q1-FY17")
     paste0("Total sales value for Quarter Q1-FY17 and Operating Group FS is ",sumval, "Million USD")
```
Shiny App running at this link


Files and repository available at




## Plot with selected information

```{r }
xyplot(Month~amtinm | Quarter*og, fltr1)
```

